### 2013-09-23 fig_mr_arfi_weight.tex
updated with all of the latest data

\begin{figure}[htb!]
\centering
\begin{tabular}{lll}
\includegraphics[width=0.3\linewidth]{figs/corr_path_vol_weight_vol} &
\includegraphics[width=0.3\linewidth]{figs/corr_weight_vol} &
\includegraphics[width=0.3\linewidth]{figs/corr_pathVol_vol} \\
(a) Path Weight : Path Volume & (b) Image Volume : Prostate Weight & (c) Image Volume : Path Volume \\
\end{tabular}
\begin{tabular}{ll}
\includegraphics[width=0.3\linewidth]{figs/corr_weight_vol_no4} &
\includegraphics[width=0.3\linewidth]{figs/corr_pathVol_vol_no4} \\
(d) Image Volume : Prostate Weight (-4) & (e) Image Volume : Path Volume (-4) \\
\end{tabular}
\caption{Tri-axial pathology measurements were used to make an ellipsoidal
    prostate volume approximation based on gross pathology axis measurements,
    which was moderately well-correlated with the excised prostated weights (a,
    R$^2$ = 0.68).  T2WI MR (blue, X) showed a moderate correlation between the
    reconstructed volumes and prostate weight (R$^2$ = 0.44), while volumes
    reconstructed from ARFI images (green, O) showed weaker correlation (R$^2$
    = 0.21) (b).  Even weaker correlations existed between both T2WI MR and
    ARFI image volumens and approaximated ellipsoidal prostate pathology
    volumes (R$^2$ = 0.08 and 0.01, respectively) (c).  It should be noted in
    these figures that Study Subject 4 had an excessively large prostate that
    was difficult to fully capture in imaging, and was therefore grossly
    underestimated in size.  We retrospectively excluded that study subject
    from the analysis and re-calculated the coefficients of determination,
    showing that MR and ARFI imaging improved to R$^2$ = 0.74 and 0.60,
    respectively, for prostate weight (d), and R$^2$ = 0.39 for both imaging
    modalities relative to pathology gross volume (e).}
\label{fig:mr_arfi_weight}
\end{figure}

>>>>

\begin{figure}[htb!]
\centering
\begin{tabular}{lll}
\includegraphics[width=0.3\linewidth]{figs/corr_path_vol_weight_vol} &
\includegraphics[width=0.3\linewidth]{figs/corr_weight_vol} &
\includegraphics[width=0.3\linewidth]{figs/corr_pathVol_vol} \\
(a) Path Weight : Path Volume & (b) Image Volume : Prostate Weight & (c) Image Volume : Path Volume \\
\end{tabular}
\begin{tabular}{ll}
\includegraphics[width=0.3\linewidth]{figs/corr_weight_vol_no4} &
\includegraphics[width=0.3\linewidth]{figs/corr_pathVol_vol_no4} \\
(d) Image Volume : Prostate Weight (-4) & (e) Image Volume : Path Volume (-4) \\
\end{tabular}
\caption{Tri-axial pathology measurements were used to make an ellipsoidal
    prostate volume approximation based on gross pathology axis measurements,
    which was moderately well-correlated with the excised prostated weights (a,
    R$^2$ = 0.68).  T2WI MR (blue, X) showed a moderate correlation between the
    reconstructed volumes and prostate weight (R$^2$ = 0.44), while volumes
    reconstructed from ARFI images (green, O) showed weaker correlation (R$^2$
    = 0.21) (b).  Even weaker correlations existed between both T2WI MR and
    ARFI image volumens and approaximated ellipsoidal prostate pathology
    volumes (R$^2$ = 0.08 and 0.01, respectively) (c).  It should be noted in
    these figures that study subject 4 had an excessively large prostate that
    was difficult to fully capture in imaging, especially in its anterior
    region, and was therefore grossly underestimated in size.  We
    retrospectively excluded that study subject from the analysis and
    re-calculated the coefficients of determination, showing that MR and ARFI
    imaging improved to R$^2$ = 0.74 and 0.60, respectively, for prostate
    weight (d), and R$^2$ = 0.39 for both imaging modalities relative to
    pathology gross volume (e).}
\label{fig:mr_arfi_weight}
\end{figure}

### 2013-09-23 results.tex
updated figures for correlation analyses and removed image comparisons to path axes
updated with all of the latest data

\begin{itemize}
    \item Images of select cases, demonstrating segmentation process
\end{itemize}

@@

The computed volumes of the prostates from the MR and ARFI imaging data are
presented in Table~\ref{tab:mr_arfi_volumes}.  The subvolumes associated with
the zonal anatomy in each imaging modality was measured
(Figure~\ref{fig:mr_arfi_volumes}(a)), showing an mean overestimation of total
prostate volume of 36.7 $\pm$ 27.9\% by ARFI imaging compared to MR volumes
(Figure~\ref{fig:mr_arfi_volumes}(b)), and central gland volumes differed
between ARFI and MR images by 2.1 $\pm$ 39.1\%
(Figure~\ref{fig:mr_arfi_volumes}(c)).

\input{tab_mr_arfi_volumes}

@@

Weights and axis measurements from the gross pathology processing of the
excised prostates were collected (Table~\ref{tab:path_data}), and using the
axis measurements (lateral-to-lateral, anterior-to-posterior, and
apex-to-base), the prostate volume was approximated as a tri-axial ellipsoid,
and its volume was estimated.

\input{tab_path_data}

MR and ARFI imaging total prostate volumes were also compared with the weights
and prostate volumes, approximated to be tri-axial ellipsoids, and calculated
from measurements of the prostate semi-principal axes.  Prostate weights were
moderately correlated with estimated pathology ellipsoidal prostate volumes
(Figure~\ref{fig:mr_arfi_weight}(a), R$^2$ = 0.68).  There was moderate
correlation between the prostate weight and the image-reconstructed prostate
volumes (Figure~\ref{fig:mr_arfi_weight}(b), R$^2$ = 0.44 (MR) and 0.21
(ARFI)), though there was weaker correlation with the ellipsoidal approximation
of the measurement prostate volume and the image-recontructed volumens
(Figure~\ref{fig:mr_arfi_weight}(c), R$^2$ = 0.08 (MR) and 0.01 (ARFI)).

@@

Measurements of the prostate dimensions along the three standard anatomic axes
(apex-to-base, lateral-to-lateral, and anterior-to-posterior) were made
(Table~\ref{tab:mr_arfi_axes}), and the correlation between the imaging axis
measurements and pathology was performed (Figure~\ref{fig:mr_arfi_path_axes}).
To evaluate the relative shape of the prostate in each imaging modality, the
relative ratios of the axes in imaging and pathology for the total prostate
volume were compared (Figure~\ref{fig:mr_arfi_total_axes}), and the relative
ratios of the central gland / zone anatomy were compared for MR and ARFI
imaging (Figure~\ref{fig:mr_arfi_central_axes}).  The mean ratio differences
between ARFI imaging, T2WI MR and pathology are compiled in
Table~\ref{tab:axis_ratio_over_under}.

\input{tab_mr_arfi_axes}

@@

\input{tab_mr_arfi_path_axes}

\input{fig_mr_arfi_total_axes}

\input{fig_mr_arfi_central_axes}

\input{tab_axis_ratio_over_under}

>>>>

@@

The subvolumes associated with the zonal anatomy in each imaging modality were
measured (Figure~\ref{fig:mr_arfi_volumes}(a)), with moderate correlation
between the ARFI and MR total prostate gland volumes (R$^2$ = 0.68), with a
mean overestimation of of 36.7 $\pm$ 27.9\% by ARFI imaging compared to MR
volumes (Figure~\ref{fig:mr_arfi_volumes}(b)).  Central gland volumes were
slightly less correlated between ARFI and MR images (R$^2$ = 0.41) with no
significant mean over/under-estimation (2.1 $\pm$ 39.1\%), but significant
variability between the cases (Figure~\ref{fig:mr_arfi_volumes}(c)).
Table~\ref{tab:mr_arfi_volumes} has the individually-measured volumes for MR
and ARFI imaging for each study subject.

@@

Weights and axis measurements from the gross pathology processing of the
excised prostates were collected (Table~\ref{tab:path_data}), and using the
axis measurements (lateral-to-lateral, anterior-to-posterior, and
apex-to-base), the prostate volume was approximated as a tri-axial ellipsoid,
and its volume was estimated (\ref{eqn:ellipsoid_volume}).  Prostate weights
were moderately correlated with estimated pathology ellipsoidal prostate
volumes (Figure~\ref{fig:mr_arfi_weight}(a), R$^2$ = 0.68).  There was moderate
correlation between the prostate weight and the image-reconstructed prostate
volumes (Figure~\ref{fig:mr_arfi_weight}(b), R$^2$ = 0.44 (MR) and 0.21
(ARFI)), though there was weaker correlation with the ellipsoidal approximation
of the measurement prostate volume and the image-reconstructed volumes
(Figure~\ref{fig:mr_arfi_weight}(c), R$^2$ = 0.08 (MR) and 0.01 (ARFI)).  Study
subject \#4 had a very large prostate, which could not be completely captured
in MR or ARFI imaging in the anterior region, so the same analyses were
performed with that study subject excluded
(Figure~\ref{fig:mr_arfi_weight}(d-e)), improving correlations for MR and ARFI
to the prostate weights (R$^2$ = 0.74 and 0.60, respectively), and prostate
volumes (R$^2$ = 0.39 for both imaging modalities).

@@

Measurements of the prostate total and central gland dimensions along the three
standard anatomic axes (apex-to-base, lateral-to-lateral, and
anterior-to-posterior) were made (Table~\ref{tab:mr_arfi_axes}), and the
correlation between the imaging axis measurements was analyzed
(Figure~\ref{fig:mr_arfi_path_axes}).  ARFI was most correlated to MR in the
lateral-to-lateral axis in both the total and central glands (R$^2$ = 0.47 and
0.44, respectively), with mean overestimates of 8.1 $\pm$ 18.4\% and 0.06 $\pm$
17.2\%, respectively (Table~\ref{tab:mr_arfi_axes_error}).  ARFI had very good
correlation with the total prostate gland axis in the anterior-to-posterior
dimension (R$^2$ = 0.58), but poor correlation in the central gland (R$^2$ =
0.00), with overestimates of 17.0 $\pm$ 12.1 and 14.8 $\pm$ 23.1\%.  ARFI
imaging had weak correlation with MR images in the apex-to-base dimension
(R$^2$ = 0.15, total gland and R$^2$ = 0.20, central gland), with differences
of 0.58 $\pm$ 12.9 and -10.8 $\pm$ 22.3\%, respectively.

@@

\input{tab_mr_arfi_axes_error}

%\input{fig_mr_arfi_total_axes}

%\input{fig_mr_arfi_central_axes}

%\input{tab_axis_ratio_over_under}
